### 2025-01-28 paper/sections/appendix.qmd
streamlined quarto bs

- **Energy Penalty** (@tbl-lin_sep-lambda_energy_exper): *ECCo* generally does yield better results than *Vanilla* for higher choices of the energy penalty (10,15) during training. *Generic* performs poorly accross the board. *Omni* seems to have an anchoring effect, in that it never performs terribly but also never as good as the best *ECCo* results. *REVISE* performs poorly across the board.
- **Cost (distance penalty)**: Results for all generators (except *Omni*) are quite bad, which can likely be attributed to extremely bad results for some choices of the **Energy Penalty** (results here are averaged). For *ECCo* and *Generic*, higher cost values generally lead to worse results.
- **Maximum Iterations**: No clear patterns recognizable, so it seems that smaller choices are ok. 
- **Validity**: *ECCo* almost always valid except for very low values during training and high values at evaluation time. *Generic* often has poor validity.
- **Accuracy**: Seems largely unaffected.

@@

@@

```{julia}
#| output: asis
get_table_inputs(df, "value"; alpha=0.9, byvars="lambda_energy_exper", backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; label="tbl-lin_sep-lambda_energy_exper", title="Results for Linearly Separable data by energy penalty.")
```

@@

@@

```{julia}
#| output: asis
get_table_inputs(df, "value"; alpha=0.9, byvars="lambda_energy_exper", backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; label="tbl-moons-lambda_energy_exper", title="Results for Moons data by energy penalty.")
```

@@

@@

```{julia}
#| output: asis
get_table_inputs(df, "value"; alpha=0.9, byvars="lambda_energy_exper", backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; label="tbl-circles-lambda_energy_exper", title="Results for Circles data by energy penalty.")
```

>>>>

@@

::: {#tbl-lin_sep-lambda_energy_exper}

@@

```{julia}
#| output: asis
get_table_inputs(df, "value"; alpha=0.9, byvars="lambda_energy_exper", backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; wrap_table=false)
```

Results for Linearly Separable data by energy penalty.

@@

::: {#tbl-moons-lambda_energy_exper}

@@

```{julia}
#| output: asis
get_table_inputs(df, "value"; alpha=0.9, byvars="lambda_energy_exper", backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs)
```

Results for Moons data by energy penalty.

@@

::: {#tbl-circles-lambda_energy_exper}

@@

```{julia}
#| output: asis
get_table_inputs(df, "value"; alpha=0.9, byvars="lambda_energy_exper", backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs)
```
